\section{JEdifAnalyze}
JEdifAnalyze performs some basic circuit analysis necessary for
subsequent executables. In particular, it performs feedback and IOB
analysis. The results of JEdifAnalyze are saved in a circuit
description file (.cdesc) required by later executables.

The following options control the feedback and IOB analysis
performed by this executable. The results of the analysis
affect the execution of later steps in the toolflow.

\begin{verbatim}
>java edu.byu.ece.edif.jedif.JEdifAnalyze
Options:
  [-h|--help]
  [-v|--version]

  <input_file>
  (-o|--output) <output>

  [--pack_registers <{i|o|b|n}>]
  [--use_bad_cut_conn]
  [--no_iob_feedback]

  [(-p|--part) <part>]

  [--write_config <config_file>]
  [--use_config <config_file>]

  [--log <logfile>]
  [--debug[:<debug_log>]]
  [(-V|--verbose) <{1|2|3|4|5}>]
  [--append_log]
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{File Options}

\subsubsection{\texttt{<input\_file>}}
Filename and path to the jedif source file to be analyzed

\subsubsection{\texttt{(-o|--output) <output\_file>}}
Filename and path to the ciruit description file (.cdesc) that will be output.

\subsection{Analysis Options}
\subsubsection{\texttt{--pack\_registers} \{i\textbar o\textbar b\textbar n\}}
By default, the BL-TMR tool treats all ports on the input EdifCell as top-level
ports (those that will be the inputs and outputs of the FPGA). The half-latch 
tool must therefore treat any FFs that will be packed into the IOBs differently
than other FFs (at least with Virtex devices). This option allows the user to
specify which IOBs the registers should be packed into: inputs (\emph{i}),
outputs (\emph{o}), both (\emph{b}), or none (\emph{n}). The default is to pack
both input and output registers.

\subsubsection{\texttt{--use\_bad\_cut\_conn}}
Use bad cutgroup connectivity graph

\subsubsection{\texttt{--no\_iob\_feedback}}
Use this option to exclude IOBs from the feedback analysis. This is useful when
a top-level inout port is involved in feedback but by design will never be 
written to and read at the same time. Thus there is no \emph{real} feedback.
Using this option may greatly reduce the amount of feedback found in the design
and thus reduce the number of voters inserted.

\input{option_Technology}
\input{option_ConfigFile}
\input{option_Logfile}


 
