\section{JEdifCutset}
\begin{verbatim}

>java edu.byu.ece.edif.jedif.JEdifCutset 
[-h|--help] 
[-v|--version] 
<input_file> 
[(-o|--output) <output_file>] 
[--ptmr <ptmr_input_file>] 
[--iob_input <input_file>] 

[--highest_fanout_cutset] 
[--highest_ff_fanout_cutset] 

[(-p|--part) <part>] 


[--log <logfile>] 
[--debug[:<debug_log>]] 
[(-V|--verbose) <{1|2|3|4|5}>] 
[--append_log]

\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{File Options}

\subsubsection{\texttt{<input\_file>}}
Filename and path to the jedif source file to be
sterilized. This is the only required parameter.

\subsubsection{\texttt{--ptmr <ptmr\_input\_file>}}
Filename and path to the tmr data file created by TMRAnalysis

Default: \texttt{<inputfile>.ptmr} in the current working directory.

\subsubsection{\texttt{(-o|--output) <output\_file>}}
Filename and path to the tmr data file appended by this tool

Default: \texttt{<inputfile>.ptmr} in the current working directory.

\subsubsection{\texttt{--iob\_input <input\_file>}}
Filename and path to the iob analysis file created by TMRAnyalysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Cutset Algorithms}
This tools can use several different algoriths to determine where to place
voters so that the voters block all the feed back in the design. 

\subsubsection{Default}
The default to to use the algorithm from previous releases

\subsubsection{\texttt{--highest\_fanout\_cutset}}
This algorithm finds the instance with the highest fanout in each SCC.
It then places a voter on this output. This algorithm has proven worse 
at reducing the number of voters between flipflops.

\subsubsection{\texttt{--highest\_ff\_fanout\_cutset}}
This algorighm finds the flipflop with the highest fanout in each SCC, and 
places a voter on the output. This algorithm has proven very good and reducing 
the number of paths that have more than one voter between flipflops.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{option_Technology}
\input{option_Logfile}
