\section{JEdifMoreFrequentVoting}
JEdifMoreFrequentVoting inserts extra voters for more frequent voting within
a design based on a logic levels threshold or a total number of desired
partitions.

At times, the user may wish to disable voter insertion on certain nets. This
can be accomplished by inserting a \texttt{`do\_not\_restore'} property on
selected nets in the .edf file as follows:\\
\texttt{(property do\_not\_restore (boolean (true)))}\\

Nets with this property will not have voters placed on them.

\begin{verbatim}
>java edu.byu.ece.edif.jedif.JEdifMoreFrequentVoting
Options:
  [-h|--help]
  [-v|--version]

  <input_file>
  (-r|--rep_desc) <rep_desc>

  [--voter_threshold <voter_threshold>]
  [--num_partitions <num_partitions>]
  [--voter_location_i voter_location_i1,voter_location_i2,...,voter_location_iN ]
  [--voter_location_n voter_location_n1,voter_location_n2,...,voter_location_nN ]

  [(-p|--part) <part>]

  [--write_config <config_file>]
  [--use_config <config_file>]

  [--log <logfile>]
  [--debug[:<debug_log>]]
  [(-V|--verbose) <{1|2|3|4|5}>]
  [--append_log]

\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{File Options}

\subsubsection{\texttt{<input\_file>}}
Filename and path to the jedif source file.

\subsubsection{\texttt{(-r|--rep\_desc) <rep\_desc>}}
Filename and path to the replication description (.rdesc) file to be modified.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Voter Options}

\subsubsection{\texttt{--voter\_threshold <voter\_threshold>}}
Voter insertion threshold. The number of instances allowed between voters.

\subsubsection{\texttt{--num\_partitions <num\_partitions>}}
The number of partitions desired in the output circuit. The partitions are
created in equal sizes, if possible. This number is currently calculated from
the maximum depth of the circuit. A more sophisticated algorithm may be
provided in the future.

\subsubsection{\texttt{--voter\_location\_i
voter\_location\_i1,voter\_location\_i2,...,voter\_location\_iN}}
Comma-separated list of instances to place voters after. Voters will be placed
on all of the nets that are outputs of the instances in the list.

\subsubsection{\texttt{--voter\_location\_n
voter\_location\_n1,voter\_location\_n2,...,voter\_location\_nN}}
Comma-separated list of nets on which to place voters.

\input{option_Technology}
\input{option_ConfigFile}
\input{option_Logfile}
